Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-20 journal/article.tex
Success: Role of POs

Some cases reported on challenges in requirements management, especially
highlighting difficulty in managing the gap between high level requirements and
stories handled by teams. It was stated that it is important that the
requirements are consise and small enough for the teams to handle [P5, P11].
It was recommended to invest in teaching skills in breaking down and writing
user stories [P11, P33, P48]. Gat [P17] describes how the gap between
development and requirements management was bridged by having a dedicated
Requirements Architect to help with requirements breakdown.

>>>>

Some cases had reported on challenges in requirements management, especially
highlighting difficulty in managing the gap between high level requirements and
stories handled by teams. It was stated that it is important that the
requirements are consise and small enough for the teams to handle [P5, P11].
It was recommended to invest in teaching skills in breaking down and writing
user stories [P11, P33, P48]. Gat [P17] describes how the gap between
development and requirements management was bridged by having a dedicated
Requirements Architect to help with requirements breakdown.

% Emphasize role of Product Owners

A particular role that seemed to make much difference in the agile introduction
was the Product Owner. Many cases reported on problems if the Product Owner did
not perform adequately, and it was seen as critical to have a dedicated person
in that role [P12, 14, P30, P39].
Success or problems emerged respectively depending on how well the Product
Owners were performing. In one case a well implemented Product Owner role was
understood to be a key success factor when using agile methods [16, P33].
It was reported that when the Product Owner role was implemented correctly the
team performed better and the work products were correct [P24]. Projects started
off better when the Product Owners were engaged early on, and some Product
Owners even became agile enthusiasts when they learned how business and
technology can collaborate in the agile model [P46].

Several cases endorsed training and coaching for the Product Owner role [P16,
P39, P46]. Product Owners should receive training on agile principles, backlog
management, user story breakdown, and agile planning [P16]. Also tool support
for backlog management and two way communication between Product Owners and
teams should be worked on [P39].
